---
title: "Joining Review Exercises"
author: "Your Name Here"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format:
  html:
    self-contained: true
    toc: true
    toc-location: left
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)

```


# Load the datasets

```{r}

counties_demographics <- readRDS(here("data", "counties_demographics.rds"))
counties_elexresults <- readRDS(here("data", "counties_elexresults.rds"))
counties_rural_urban_suburban <- readRDS(here("data", "counties_rural_urban_suburban.rds"))



```

# Exercises

Join together the election results and urban/suburban/rural tables above, and then use the merged table to:

-   filter for just Virginia

-   group/summarize to calculate the mean pct of Trump 2020 vote by urban/rural categories

```{r}
joined_counties <- inner_join(counties_elexresults, counties_rural_urban_suburban, by = "geoid")

joined_counties_virginia <- joined_counties %>% 
  filter(state_code == "VA")
###asdfasdfsadf

```

```{r}
va_trumpvote_byurbanrural <- joined_counties_virginia %>% 
  group_by(rural_urban) %>% 
  summarise(mean_vote_percentage = mean(pct_r_2020))

va_trumpvote_byurbanrural

```

Take the grouped dataset, and create a column chart using ggplot to display it

```{r}

ggplot(va_trumpvote_byurbanrural, aes(x = reorder(rural_urban, mean_vote_percentage), y = mean_vote_percentage)) + 
  geom_col(fill = "darkred") +
  coord_flip() +
  scale_y_continuous(name = "Avg Pct of Vote", labels = scales::comma) +
  scale_x_discrete(name = "Type of County") +
  labs(title = "Trump Percent of the Vote in Virginia ", 
       subtitle = "Average in Urban/Suburban/Rural Counties") +
  theme_minimal() #

```

Now using the joined dataset, come up with two groupings you find interesting or newsworthy in a particular state, and replicate the steps above them them instead.

(i.e. instead of for urban/rural, perhaps you want to look at pct of white college grads in Michigan, etc. If you're having trouble, you can stick with Virginia as your state.)

```{r}




```


```{r}





```
