---
title: "Intro to Functions"
author: "Aaron Kessler"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format:
  html:
    self-contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```

what is a function??

All functions have the same structure:

`myfunctionname <- function(argument1, argument2, … ){`

`**allmycode goes here! with argument names in place of values!**`

`return(object)`

`}`

Let's see a basic example of this:

```{r}


cube_me <- function(mynumber){
  
  result <- mynumber ^ 3
    
    return(result)
}
```

Now we'll run the function:

```{r}

cube_me(5)

```

When doing these things, try to first figure out the thing you're trying to solve. 
And then, turn it into a function.  
 
For example, what if we want to say a sports team stinks.

```{r}

stinker_phrase <- "The Cowboys stink!"

stinker_phrase

```
Now let's say we want to separate out the name of the team into its own
variable so we can change it.

```{r}

teamname <- "Cowboys"

stinker_phrase <- paste0("The ", teamname, " stink!")

stinker_phrase

#Change the team name above and re-run, see what happens.
```

Now we can make this into a function.

```{r}
# let's try another

stinkerteam_function <- function(teamname){
  
  result <- paste0("The ", teamname, " stink!")
  
  return(result)
}
```

```{r}
stinkerteam_function("Cowboys")

stinkerteam_function("Jets")
```

Now let's try a function with TWO arguments instead of one
```{r}

twoteam_function <- function(myteam, otherteam){
  
  result <- paste0("The ", myteam, " are going to wipe the floor with the ", otherteam)
  
  return(result)
}
```

```{r}

twoteam_function("Eagles", "Cowboys")


```

Finnaly, we can we automate by feeding of list of multiple teams
```{r}

myteams_vector <- c("Eagles", "Phillies", "Flyers")

otherteams_vector <- c("Cowboys", "Astros", "Stars")

#run function
twoteam_function(myteams_vector, otherteams_vector)


```
